Relationships in the extremes and their influence on competition and coexistence: Supporting information

### 2022-01-25 paper/SupMat.Rnw
working on edits of SI section 9, not done yet

The decomposition of storage effects and quantification of contributions of ATAs depends on 
the removal of asymmetric tail associations from the bivariate distribution
$(E_i,C_{i \bs i})$ while maintaining its correlation and marginal distributions.
In the Theory section of the main text, we decribed methods for this removal process
when the distributions of $E_i$ and $C_{i \bs i})$ are explicitly known, but for the 
diatom example explored for goal G4 of the main text (see also SI section \ref{}), 
we only have samples of $E_i$ and $C_{i \bs i})$

;
a modified distribution $E_i^\nat$ and $C_{i \bs i}^\nat$

>>>>

The decomposition of storage effects and quantification of contributions of ATAs depends on 
the removal of asymmetric tail associations from the bivariate random variable
$(E_i,C_{i \bs i})$, while maintaining its correlation and marginal distributions, to produce a new
random variable $(E_i^\nat,C_{i \bs i}^\nat)$.
In the Theory section of the main text, we decribed this removal process
when the distributions of $E_i$ and $C_{i \bs i})$ are explicitly known, but for the 
diatom example explored for goal G4 of the main text (see also SI section \ref{sect:diatom_model}), 
we only have samples from $(E_i,C_{i \bs i})$, based on simulations. We here describe how to
produce a sample from $(E_i^\nat,C_{i \bs i}^\nat)$ in this modified context.
